---
title: "Debug Dummy"
author: "Faizan Khalid Mohsin"
date: "July 29, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r }

require(readxl)
require(dplyr)

```

So in column F i need to create 16 dummys that represent all possible situation for each ID and calculate the acombying time in column c then total them where column G says "END"

I created the dummys manually (column H to W) in the sample attached and created the if formula but unable to create formula that sum all above cell up to the cell where it says "END" in column C. if you want you can erase these dummys  and create the whole process in R or if you know how to do it in excel then sure.

I need this by tomorrow
expect 15 min spend on this query


```{r , echo=FALSE}

data = read_excel("Dummy1.xlsx")
data_final = data

# for (i in 8:22){
#   
#   data_final[, i] = as.numeric( as.character(data_final[,i] ))
#   
# }

cols <- sapply(data, is.logical)
data_final[,cols] <- lapply(data[,cols], as.numeric)

```


```{r}
str(data)
str(data_final)
```






```{r}

for ( i in unique(data$ID)){
  #i = 1
  
  data_1 = subset(data, process_end != "END")
  
  data_id = filter(data_1, ID == i)
  
  sum_data_id = as.numeric(colSums( data_id[, 8:22], na.rm = T ))
  
  names_data = names(data_id[, 8:22])
  

  #str(sum_data_id)
  sum_data_id_2 = matrix(sum_data_id, nrow = 1, ncol = 15)
  
  colnames(sum_data_id_2) = names_data
  
  #str(sum_data_id_2)
  
  sum_data_id_3 = as.data.frame(sum_data_id_2)
  #str(sum_data_id_3)
  data_final[data$ID == i & data$process_end == "END", 8:22 ] = sum_data_id_3
  
  
  #final = data[data$ID == i & data$process_end == "END", 8:22 ] 
}

#data_final[which(data_final == FALSE, arr.ind = T)] = 0

write.csv(data_final, "data_final.csv", row.names = F)

```


```{r method 2}

final = data %>% group_by(ID, Historical_Step_Name) %>% summarise(total_process_time = sum(Historical_Step_Status.Duration)) 
final = final[order(final$ID, final$Historical_Step_Name), ]

```
